\section{Experimental Setup}

\paragraph{Data.} We train on AffectNet~\cite{mollahosseini2017affectnet}
(images with continuous VA) and use AFEW-VA~\cite{kossaifi2017afew} (per-frame VA
from video) as the distribution-shift test set; RAF-DB serves as a secondary
robustness check. All splits are deterministic and seeded. Datasets are
registration-gated and are not redistributed; a synthetic generator reproduces
the full pipeline for continuous integration.

\paragraph{Metrics.} \emph{Accuracy:} concordance correlation coefficient (CCC)
for valence and arousal, plus RMSE/MAE. \emph{Calibration:} regression ECE via
quantile calibration, and sharpness. \emph{Selective prediction:} risk--coverage
and accuracy--rejection curves, summarised by the area under the risk--coverage
curve (AURC). \emph{Shift:} calibration degradation and the AUROC of separating
in-distribution from shifted inputs by the uncertainty score. Our primary shift
is corruption-based --- blur, noise, brightness, contrast, and JPEG artefacts
applied to the AffectNet test set in the spirit of ImageNet-C --- giving a genuine
in-distribution$\rightarrow$shifted comparison on identical images and labels with
no second dataset; an optional cross-dataset shift to AFEW-VA reuses the same
harness where that (registration-gated) data is available.
\emph{Conformal:} empirical coverage versus the $1-\alpha$ target on in-dist and
shifted data.

\paragraph{Reproducibility.} Every result traces to a YAML config, a seed, and a
file under \texttt{results/}; \texttt{make repro} regenerates all tables and
figures, including the ones \texttt{\textbackslash input} into this paper.
