\section{Method}

\subsection{Backbone and heads}
A shared visual encoder (a timm CNN; ResNet-50 unless stated) maps an aligned
face crop to a feature vector. We compare three heads, all predicting VA in
$[-1,1]^2$:
\begin{itemize}
  \item \textbf{Regression} (baseline): a deterministic point estimate trained
        with MSE; no native uncertainty.
  \item \textbf{Gaussian} (heteroscedastic): predicts a mean and variance per
        dimension, trained with the Gaussian negative log-likelihood; captures
        aleatoric uncertainty.
  \item \textbf{Evidential} (primary): deep evidential
        regression~\cite{amini2020evidential} places a
        Normal--Inverse--Gamma prior over each VA dimension, yielding parameters
        $(\gamma,\nu,\alpha,\beta)$ and thus both aleatoric variance
        $\beta/(\alpha-1)$ and epistemic variance $\beta/(\nu(\alpha-1))$ from a
        single forward pass.
\end{itemize}

\subsection{Uncertainty wrappers}
At evaluation time we additionally consider MC-Dropout~\cite{gal2016dropout}
($N$ stochastic passes) and deep ensembles~\cite{lakshminarayanan2017simple}
($K$ independently seeded models), whose disagreement estimates epistemic
uncertainty.

\subsection{Split conformal calibration}
Building on split conformal prediction~\cite{vovk2005algorithmic} and calibrated
regression~\cite{kuleshov2018calibrated}, given a held-out calibration set we
compute variance-normalised nonconformity
scores $s_i = |y_i - \hat\mu_i| / \hat\sigma_i$ and take the
$\lceil (n{+}1)(1-\alpha)\rceil/n$ empirical quantile $q$. The prediction
interval $\hat\mu \pm q\,\hat\sigma$ then has coverage $\ge 1-\alpha$ on
exchangeable data. The mean half-width supplies the abstention threshold used by
the demonstrator, so the deployed system and the reported experiments share one
calibrated bound.

\subsection{rPPG as a gated second modality}
We extract a pulse signal from the face ROI with the POS
algorithm~\cite{wang2017pos} and a signal-quality score. The quality score multiplicatively gates the rPPG feature:
a low-quality pulse contributes near zero and \emph{raises} predictive
uncertainty rather than injecting a confident guess. This honesty constraint is
enforced in the fusion layer, not left to the optimiser.
